Refinements for open pNets

### 2021-07-23 2021-Refinement/paper/refinementarticle.tex
initial push: composition

@@

@@

\subsection{Example}

As an example, the traffic light system  that controls  
 traffic at the intersection of a busy highway. The open automaton  
modeling this system  is illustrated in  Figure \ref{fig:tls}. This automaton has three states  remembering which coloured light
is on (Red, Yellow or Green). It includes two holes: a controller ($\symb{ctl}$) and a counter ($\symb{cnt}$)  depicting together the behaviour of the timer. The color switches when the counter and the controller component agree that the time is over. The new time limit can be set by the counter component and the exposed action to the environment is an unobservable  action $\tau$.

>>>>

\TODO{useful or not?}
\begin{definition}[Guard, Out-transition, Transition variables]
Let \(V\) be the variable names of the considered automaton, \(T\) its transitions and \(r\) one of its states.
\(\fOT[T]{r} \in T\) are called the out-transitions of the state \(r\).
\(\fIT[T]{r} \in T\) are called the in-transitions of the state \(r\).
When the transition set is clear from the context, it will be omitted.
The local variables of a transition \(\fvars{t}\) are all variables appearing in transition \(t\) except the global variables of the automaton.
\begin{align*}
	\fOT[T]{r} & ::= \mset{\OTg \in T}{s = r} &
	\fIT[T]{r} & ::= \mset{\OTg \in T}{s' = r} \\
\end{align*}
\vspace{-1cm}
\begin{gather*}
	\fguard{\OTg} ::= g \\
	\fvars{\OTg} ::= \mpar{\fvars{\alpha} \cup \fvars{g} \cup \bigcup_{j \in J'} \fvars{\beta_j} \cup \bigcup_{v \in V} \fvars{\psi\mpar{v}}} \setminus V
\end{gather*}
\end{definition}

@@

Open automata are partially specified automata, that partiality comes mostly from the holes.
A hole is an interface in which we can plug an open automaton.
The plugging operation is called composition.
The composition of open automata was already implicitly defined by the means of composition on pNets in previous work \cite{henrio:01299562} but never completely formalised on open automata.
The definition of composition below is a direct translation of what happens with pNets composition without the need of introducing pNets.
\begin{definition}[Composition of open automata]
The composition of \(A_c = \OAg[c]\) in the hole \(k \in J_p\) of \(A_p = \OAg[p]\) gives the open automaton defined as follows.
\begin{align*}
	A_p\subst{A_c}{k} ::= & \OA{S_p \times S_c}{\mpar{s_{0p}, s_{0c}}}{V_p \uplus V_c}{\sigma_{0p} \uplus \sigma_{0c}}{J_c \uplus J_p \setminus \mbrc{k}}{T} \\
	\text{with } T = & \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s'_c}}{\alpha_p}{\beta_j^{j \in J'_c \uplus J'_p \setminus \mbrc{k}}}{g_p \wedge g_c \wedge \alpha_c = \beta_k}{\psi_p \uplus \psi_c}}{\OTx{p}{}{}{p} \in T_p, \OTx{c}{}{}{c} \in T_c} \\
	& \cup \mset{\OT{\mpar{s_p, s_c}}{\mpar{s'_p, s_c}}{\alpha_p}{\beta_j^{j \in J'_p}}{g_p}{\psi_p}}{\OTx{p}{}{}{p} \in T_p, k \notin J'_p, s_c \in S_c}
\end{align*}
\end{definition}
The action emitted when \(A_c\) makes a transition is synchronised with the action of the hole \(k\) in transitions of \(A_p\) which have it as a hole action (first transition set, \(\alpha_c = \beta_k\)).
The composition may look like a handshake, with both automata running in parallel (product of states and joint variables) however it is asymmetric:
The first automaton decides when the second can evolve by involving it in a transition, while the first automaton can evolve independently as soon as the hole is not involved in an open transition.

@@

TODO OR NOT?

\subsection{Example}
\newcommand\symb[1]{\TODO{#1}}
As an example, the traffic light system  that controls  
 traffic at the intersection of a busy highway. The open automaton  
modeling this system  is illustrated in  Figure \ref{fig:tls}. This automaton has three states  remembering which coloured light
is on (Red, Yellow or Green). It includes two holes: a controller ($\symb{ctl}$) and a counter ($\symb{cnt}$)  depicting together the behaviour of the timer. The color switches when the counter and the controller component agree that the time is over. The new time limit can be set by the counter component and the exposed action to the environment is an unobservable  action $\tau$.
